\vskip-0.6in \Large Political Uncertainty

### 2015-04-07 GS-extension.tex
fixed typo on line 298; verified chain rule is correct (line 322)
correct obj fcn (add WTP and cost) and push through
add notes from chat with Frank 4/3 and calculate logistic version of FOC

			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(z) \right)$, $\Phi\left(- \alpha + b(z) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(z) \right)$

@@

					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\

@@

					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right)

@@

					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\

@@

					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)

@@

					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\

@@

					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0

@@

					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)+ \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\
					- 2\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0

@@

			Further:

@@

					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \\ \left[ \Phi\left(- \alpha + b(0) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \right] = 0

@@

			So I think we have three conditions:
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) = 0
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0

>>>>

			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)$, $\Phi\left(- \alpha + b(0) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)$

@@

					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\

@@

					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)

@@

					W_B \biggl[ \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\

@@

					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)

@@

					W_B \biggl[ \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\

@@

					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1

@@

					W_B \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \biggl[ \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - 
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1

@@

			Simplifying further:

@@

					- 2\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\right)^2}{2}} }
					\label{eq:firstfoc}

@@

			The two symmetric conditions would be:
			\begin{multline}
					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
				\end{multline}
			\begin{multline}
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
				\end{multline}
		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
			\item Need to check SOC at some point
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
		\end{itemize}
	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
		\begin{equation}
					\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}} + \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}
					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)} }
				\end{equation}
\end{itemize}
